Inferential Analysis of the \\ Supreme Court Citation Network

### 2018-04-30 Tex/presentations/SPSA2018/DesmaraisSPSATalk.tex
revised network theory section

\begin{frame} \frametitle{Two Limitations in Case-Level Analysis}
\Large
\begin{enumerate}
\item {\bf Theoretical:} Cannot learn about relational processes
\\~\\
\item {\bf Methodological:} Risk bias from omitted structure
\end{enumerate}

@@

\begin{frame} \frametitle{DAG[gish] Dynamics}
\centering

@@

    Reciprocity &  Transitivity \\
\includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/mutual_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/triangle_coef_trend.pdf} \\

     Activity & Popularity \\
\includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/o2star_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/i2star_coef_trend.pdf} \\

@@

 \begin{tabular}{cc}
  MQ Score Difference & Ideological Breadth \\
\includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/mq_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/absdiffmq_coef_trend.pdf} \\

   Same Issue &  Majority Size \\
\includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/sameissue_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/numberjusticespro_coef_trend.pdf} \\

@@

>>>>

\begin{frame} \frametitle{Two Limitations to Case-Level Analysis}
\Large
\begin{enumerate}
\item {\bf Theoretical:} Cannot learn about relational processes
\\~\\
\item {\bf Methodological:} Risk bias from omitted structure
\end{enumerate} ~\\

We propose a dyadic, network-analytic approach

@@

\begin{frame} \frametitle{ The Citation TERGM: $C_t|C_{<t}$ via $h(C_{\leq t})$}
\centering

@@

    Reciprocity &  Transitivity \\
\includegraphics[width = 0.55\textwidth, trim= .5cm 1cm 0.5cm .45cm,clip=true]{../../images/mutual_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= .5cm 1cm 0.5cm .45cm,clip=true]{../../images/triangle_coef_trend.pdf} \\

     Activity & Popularity \\
\includegraphics[width = 0.55\textwidth, trim= .5cm 1cm 0.5cm .45cm,clip=true]{../../images/o2star_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= .5cm 1cm 0.5cm .45cm,clip=true]{../../images/i2star_coef_trend.pdf} \\

@@

 \begin{tabular}{cc}
  MQ Score Difference & Ideological Breadth \\
\includegraphics[width = 0.55\textwidth, trim= .5cm 1cm 0.5cm .45cm,clip=true]{../../images/mq_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= .5cm 1cm 0.5cm .45cm,clip=true]{../../images/absdiffmq_coef_trend.pdf} \\

   Same Issue &  Majority Size \\
\includegraphics[width = 0.55\textwidth, trim= .5cm 1cm 0.5cm .45cm,clip=true]{../../images/sameissue_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= .5cm 1cm 0.5cm .45cm,clip=true]{../../images/numberjusticespro_coef_trend.pdf} \\

@@

\begin{itemize}

\item Randomly split dyads 80/20 into training and test
\item Estimate models using training, predict test
\item Repeat 10 times

\end{itemize}
~\\
